Behavior Driven Development in Haskell

### 2012-10-20 paper.tex
Shorten abstract

\begin{abstract}
We observe that several widely used Haskell libraries do not have
tests.  Test code assists developers in maintaining correctness when
extending software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools: Doctest for user
documentation and Hspec for code documentation.  Our approach can be
used for design, documentation and automated testing.  We hope that
this motivates Haskell programmers to write more and better tests.
\end{abstract}

>>>>

\begin{abstract}
Several widely used Haskell libraries do not have tests.  Test code
assists developers in maintaining correctness when extending software,
and shows users how an API is supposed to be used.

We show how to do behavior-driven development in Haskell with two
tools: Doctest and Hspec.  Our approach can be used for design,
documentation and automated testing.  We hope that this motivates
Haskell programmers to write more and better tests.
\end{abstract}
